### 2016-05-27 R/ITHIM.Rmd
Update to ITHIM.Rmd

### Instanciation

@@

RR <- createActiveTransportRRs()

nAgeClass <- 8

totalMETs.baseline <- mapply("+",ITHIM.baseline$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)
totalMETs.scenario <- mapply("+",ITHIM.scenario$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)

totalMETs.baseline <- lapply(totalMETs.baseline, function(x) ifelse(x<2.5,0.1,x))
totalMETs.scenario <- lapply(totalMETs.scenario, function(x) ifelse(x<2.5,0.1,x))

## RR for Females and Breast Cancer
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)
RR.baseline <- RR^(totalMETs.baseline$F^0.5)
RR.scenario <- RR^(totalMETs.scenario$F^0.5)
diseaseBurden <- RR.baseline/RR.scenario
burden <- 1 - (rowSums(diseaseBurden)-ncol(diseaseBurden))/rowSums(diseaseBurden)
(AF <- 1 - burden)
```

```{r ITHIM}
ITHIM <- ITHIM.baseline
names(ITHIM)
```

For help run the following.
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```

>>>>

### Running in R

@@

totalMETs.baseline <- mapply("+",ITHIM.baseline$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)
totalMETs.scenario <- mapply("+",ITHIM.scenario$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)
totalMETs.baseline <- lapply(totalMETs.baseline, function(x) ifelse(x<2.5,0.1,x))
totalMETs.scenario <- lapply(totalMETs.scenario, function(x) ifelse(x<2.5,0.1,x))
```
Now we can compute the attributable fraction (AF).

```{r RRs}
## RR for Females and Breast Cancer
RR <- createActiveTransportRRs()
nAgeClass <- 8
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)
RR.baseline <- RR^(totalMETs.baseline$F^0.5)
RR.scenario <- RR^(totalMETs.scenario$F^0.5)
diseaseBurden.scenario <- RR.baseline/RR.scenario
diseaseBurden.baseline <- RR.baseline/RR.baseline # What!
(AF <- (rowSums(diseaseBurden.scenario)-rowSums(diseaseBurden.baseline))/rowSums(diseaseBurden.scenario))
```

```{r explore}
names(ITHIM.baseline$parameters)
```

We use Rws to estimate mean walking speed and from that mean walking
METs.  Mean cycling METs, however, is constant and is not a function
of mean cycling speed or Rcs.  So, I do not think Rcs is currently
used.

To see the help page for a function use help().
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```
